### 2021-01-16 appendix.tex
Minor changes.

\section{Relation to Priority CP}
\begingroup
\usingnamespace{pcp}

@@

\begin{compacttheorems}
    \begin{restatabledefinition}{defpcpactions}[Actions]
    A~process acts on an endpoint $\tm{x}$ if it is of the form $\tm{\link{x}{y}}$, $\tm{\link{y}{x}}$, $\tm{\send{x}{y}{P}}$, $\tm{\recv{x}{y}{P}}$, $\tm{\close{x}{P}}$, $\tm{\wait{x}{P}}$, $\tm{\inl{x}{P}}$, $\tm{\inr{x}{P}}$, $\tm{\offer{x}{P}{Q}}$, or $\tm{\absurd{x}}$. A~process is an action if it acts on some endpoint $\tm{x}$.
  \end{restatabledefinition}
  \begin{restatabledefinition}{defpcpcanonicalforms}[Canonical Forms]
    \label{def:pcp-canonical-forms}
    A~process $\tm{P}$ is in canonical form if it is of the form $\tm{\halt}$ or $\tm{\res{x_1}{x'_1}{\dots\res{x_n}{x'_n}{(P_1 \parallel\dots\parallel P_m)}}}$ where $m>0$ and each $\tm{P_j}$ is an action.
  \end{restatabledefinition}
  \begin{restatablelemma}{lempcpcanonicalforms}[Canonical Forms]
    \label{lem:pcp-canonical-forms}
    If $\seq{P}{\ty{\Gamma}}$, there exists some $\tm{Q}$ such that $\tm{P}\equiv\tm{Q}$ and $\tm{Q}$ is in canonical form.
  \end{restatablelemma}
  \begin{proof}
    If $\tm{P}=\tm{\halt}$, we are done. Otherwise, we move any $\nu$-binders to the top using \LabTirName{SC-ResExt}, and discard any superfluous occurrences of $\tm{\halt}$ using \LabTirName{SC-ParNil}.
  \end{proof}
  \restatetheorem{thmpcpclosedprogress}
  \input{prf/thm-pcp-closed-progress}
\end{compacttheorems}
\endgroup

\subsubsection*{Translation}
\begingroup
\restatelemma{lempcptopgvtermspreservation}
\input{prf/lem-pcp-to-pgv-terms-preservation}

>>>>

\section{Relation to Priority CP}
\begingroup
\usingnamespace{pcp}
\subsection{Revisiting Priority CP}

@@

\begin{compacttheorems}
    \begin{restatabledefinition}{defpcpactions}[Actions]
    A~process acts on an endpoint $\tm{x}$ if it is $\tm{\link{x}{y}}$, $\tm{\link{y}{x}}$, $\tm{\send{x}{y}{P}}$, $\tm{\recv{x}{y}{P}}$, $\tm{\close{x}{P}}$, $\tm{\wait{x}{P}}$, $\tm{\inl{x}{P}}$, $\tm{\inr{x}{P}}$, $\tm{\offer{x}{P}{Q}}$, or $\tm{\absurd{x}}$. A~process is an action if it acts on some endpoint $\tm{x}$.
  \end{restatabledefinition}
  \begin{restatabledefinition}{defpcpcanonicalforms}[Canonical Forms]
    \label{def:pcp-canonical-forms}
    A~process $\tm{P}$ is in canonical form if it is $\tm{\halt}$ or $\tm{\res{x_1}{x'_1}{\dots\res{x_n}{x'_n}{(P_1 \parallel\dots\parallel P_m)}}}$ where $m>0$ and each $\tm{P_j}$ is an action.
  \end{restatabledefinition}
  \begin{restatablelemma}{lempcpcanonicalforms}[Canonical Forms]
    \label{lem:pcp-canonical-forms}
    If $\seq{P}{\ty{\Gamma}}$, there exists some $\tm{Q}$ such that $\tm{P}\equiv\tm{Q}$ and $\tm{Q}$ is in canonical form.
  \end{restatablelemma}
  \begin{proof}
    If $\tm{P}=\tm{\halt}$, we are done. Otherwise, we move any $\nu$-binders to the top using \LabTirName{SC-ResExt}, and discard any superfluous occurrences of $\tm{\halt}$ using \LabTirName{SC-ParNil}.
  \end{proof}
  \restatetheorem{thmpcpclosedprogress}
  \input{prf/thm-pcp-closed-progress}
\end{compacttheorems}
\endgroup

\subsection{Translation}
\begingroup
\restatelemma{lempcptopgvtermspreservation}
\input{prf/lem-pcp-to-pgv-terms-preservation}
